\chapter{Problem Definition}

In the contemporary digital landscape, the way individuals seek romantic connections has evolved significantly. With the proliferation of online dating platforms, there is a growing demand for user-friendly and efficient solutions that facilitate meaningful interactions among individuals. Recognizing this need, our project aims to develop a dating website using HTML, CSS, and JavaScript to provide a platform for users to discover potential matches based on shared interests and preferences.
\section{Objectives:}
\begin{itemize}
    \item \textbf{Create a User-Friendly Interface:} Our primary objective is to design and implement a user-friendly interface that allows users to input their personal details easily and navigate the website seamlessly.
    \item \textbf{Implement Secure Login Mechanism:} We aim to incorporate a secure login mechanism to ensure that registered users can access their accounts securely. Additionally, we will provide a password recovery system for users who forget their passwords.
    \item \textbf{Facilitate Profile Matching:} Our project will focus on implementing algorithms to match user profiles based on shared interests and hobbies. We will develop criteria to determine the "right match" for each user and present matched profiles accordingly.
    \item \textbf{Enhance User Experience:} We strive to enhance the overall user experience by incorporating features such as scrolling/swiping through profiles, liking/rating profiles, applying filters, and providing an option to contact matched profiles via email.
\end{itemize}

\section{Scope:}
\begin{itemize}
    \item Our project will focus on developing the core functionalities of the dating website, including the login page, input interface, profile matching algorithms, and output interface.
    \item We will utilize predefined student profiles stored in a JSON file named students.json to simulate user interactions and profile matching.
    \item Customisations beyond the basic tasks will be explored to enhance the functionality and user experience of the website.
\end{itemize}





